---
title: "Difference in Difference"
author: "Gary Nguyen"
---

## 1. Load Libraries

```{r load_library}
library(tidyverse)
library(here)
library(lubridate)
library(janitor)
library(zoo)
library(ggthemes)

library(forecast)
library(stargazer)
library(data.table)
library(tableone)
library(lattice)
library(pwr)
library(rcompanion)
library(scales)
library(plm)
library(readxl)
library(MatchIt)
library(lfe)
library(Synth)
library(gsynth)
library(panelView)
library(CausalImpact)
```

```{r devtools_loadall}
devtools::load_all()
```

## 2. Load and Process Data

```{r load_data}
metrics <- readr::read_csv(file.path(here::here(), 'data/data.csv'))
property <- readr::read_csv(file.path(here::here(), 'data/property_info.csv'))
```

```{r process_data}
metrics <- metrics %>% 
  clean_names() %>% 
  replace(is.na(.), 0)

property <- property %>% 
  clean_names() %>% 
  dplyr::rename(online_visits = virtual_reality_launched) %>% 
  mutate(avg_review_rating_num = case_when(
    avg_review_rating == "< 2.5" ~ (0 + 2.5)/2,
    avg_review_rating == "2.5 - 3" ~ (2.5 + 3)/2,
    avg_review_rating == "3.1 - 3.5" ~ (3.1 + 3.5)/2,
    avg_review_rating == "3.6 - 4" ~ (3.6 + 4)/2,
    avg_review_rating == "4.1 - 4.25" ~ (4.1 + 4.25)/2,
    avg_review_rating == "4.26 - 4.50" ~ (4.26 + 4.5)/2,
    avg_review_rating == "4.51 - 4.75" ~ (4.51 + 4.75)/2,
    avg_review_rating == "4.76+" ~ (4.76 + 5)/2,
    avg_review_rating == "No Reviews" ~ 0 
  )) %>% 
  mutate(number_of_reviews_on_the_property_num = case_when(
    number_of_reviews_on_the_property == "20+"  ~ 20,
    number_of_reviews_on_the_property == "6 to 11" ~ (6 + 11)/2,
    number_of_reviews_on_the_property == "5" ~ 5, 
    number_of_reviews_on_the_property == "12 to 19" ~ (12 + 19)/2,
    number_of_reviews_on_the_property == "4" ~ 4,
    number_of_reviews_on_the_property == "2" ~ 2,
    number_of_reviews_on_the_property == "0" ~ 0,
    number_of_reviews_on_the_property == "3" ~ 3,
    number_of_reviews_on_the_property == "1" ~ 1
  )) %>% 
  mutate(treat = if_else(online_visits == 'Yes', 1, 0))

common_property_id <- intersect(
  property %>% pull(property_id) %>% unique(),
  metrics %>% pull(property_id) %>% unique()
  )

property <- property %>% 
  filter(property_id %in% c(common_property_id))

property_metrics <- metrics %>% 
  left_join(property, by = 'property_id') 

property_FL <- property %>% 
  filter(location == 'Destin, Florida')

property_TX <- property %>% 
  filter(location == 'Austin, Texas')

property_NV <- property %>% 
  filter(location == 'Vegas, Nevada')
```

## 3. Difference in Difference

```{r to_test}
to_test <- metrics %>% 
  left_join(property, by = 'property_id') %>% 
  mutate(post = if_else(date >= as.Date('2019-01-01'), 1, 0)) %>% 
  dplyr::select(
    property_id, 
    avg_review_rating_num, 
    number_of_reviews_on_the_property_num,
    instant_booking_enabled,
    premier_partner_badge, 
    maximum_occupancy,
    bedrooms,
    bathrooms,
    post,
    treat,
    bookings, 
    booking_amount, 
    booking_requests,
    number_of_times_the_property_got_displayed_in_search_page,
    number_of_photos_of_the_property_on_the_property_page,
    property_page_views_visits
  ) %>% 
  mutate_all(as.numeric)
```

Statistically significant features for `bookings`:

* `premier_partner_badge` (-0.003)
* `bathrooms` (-0.001)
* `post` (0.029)
* `post:treat` (-0.007)

```{r did_bookings}
f_did <- lm(data = to_test, 
            booking_requests ~ avg_review_rating_num + number_of_reviews_on_the_property_num + instant_booking_enabled + premier_partner_badge + maximum_occupancy + bedrooms + bathrooms + number_of_photos_of_the_property_on_the_property_page + post + treat + post*treat)
stargazer(f_did, type = 'text', report = ('vc*p'))
```

Statistically significant features for `booking_amount`:

* `bedrooms` (3.189)
* `bathrooms` (-3.887)
* `post` (60.822)

```{r did_booking_amount}
f_did <- lm(data = to_test, 
            booking_amount ~ avg_review_rating_num + number_of_reviews_on_the_property_num + instant_booking_enabled + premier_partner_badge + maximum_occupancy + bedrooms + bathrooms + number_of_photos_of_the_property_on_the_property_page + post + treat + post*treat)
stargazer(f_did, type = 'text', report = ('vc*p'))
```

Statistically significant features for `booking_requests`:

* `premier_partner_badge` (-0.003)
* `bathrooms` (-0.001)
* `post` (0.029)
* `post:treat` (-0.007)

```{r did_booking_requests}
f_did <- lm(data = to_test, 
            booking_requests ~ avg_review_rating_num + number_of_reviews_on_the_property_num + instant_booking_enabled + premier_partner_badge + maximum_occupancy + bedrooms + bathrooms + number_of_photos_of_the_property_on_the_property_page + post + treat + post*treat)
stargazer(f_did, type = 'text', report = ('vc*p'))
```

Statistically significant features for `property_page_views_visits`:

* `number_of_reviews_on_the_property_num` (+0.065)
* `instant_booking_enabled` (+0.495)
* `maximum_occupancy` (-0.096)
* `bedrooms` (+0.555)
* `bathrooms` (-0.284)
* `number_of_photos_of_the_property_on_the_property_page` (-0.040)
* `post` (+6.653)
* `treat` (-0.890)
* `post:treat` (-0.912)

```{r did_property_page_views_visits}
# bookings
# booking_amount
# booking_requests
# number_of_times_the_property_got_displayed_in_search_page
# property_page_views_visits

f_did <- lm(data = to_test, 
            property_page_views_visits ~ avg_review_rating_num + number_of_reviews_on_the_property_num + instant_booking_enabled + premier_partner_badge + maximum_occupancy + bedrooms + bathrooms + number_of_photos_of_the_property_on_the_property_page + post + treat + post*treat)
stargazer(f_did, type = 'text', report = ('vc*p'))
```

```{r did_number_of_times_the_property_got_displayed_in_search_page}
# bookings
# booking_amount
# booking_requests
# number_of_times_the_property_got_displayed_in_search_page
# property_page_views_visits

f_did <- lm(data = to_test, 
            number_of_times_the_property_got_displayed_in_search_page ~ avg_review_rating_num + number_of_reviews_on_the_property_num + instant_booking_enabled + premier_partner_badge + maximum_occupancy + bedrooms + bathrooms + number_of_photos_of_the_property_on_the_property_page + post + treat + post*treat)
stargazer(f_did, type = 'text', report = ('vc*p'))
```
