---
title: "Propensity Score Matching"
author: "Gary Nguyen"
---

In this notebook, I performed statistical tests as if the dataset was generated from a randomized controlled experiment (such as an AB Test).

## 1. Load Libraries

```{r load_library}
library(tidyverse)
library(here)
library(lubridate)
library(janitor)
library(zoo)
library(ggthemes)

library(forecast)
library(stargazer)
library(data.table)
library(tableone)
library(lattice)
library(pwr)
library(rcompanion)
library(scales)
library(plm)
library(readxl)
library(MatchIt)
library(lfe)
library(Synth)
library(gsynth)
library(panelView)
library(CausalImpact)
library(optmatch)

library(zeallot)
```

```{r devtools_loadall}
devtools::load_all()
```

## 2. Load and Process Data

```{r load_data}
c(metrics, property) %<-% get_property_data()
```

## 3. T-test (aggregated)

```{r control_ids}
control_ids <- property %>% 
  filter(treat == 0) %>% 
  pull(property_id) %>% 
  unique()
```

```{r resample}
df_for_test <- metrics %>% 
  mutate(treatment = if_else(property_id %in% control_ids, 0, 1)) %>% 
  mutate(post = if_else(date < as.Date('2019-01-01'), 'Pre', 'Post')) %>% 
  group_by(property_id, post, treatment) %>% 
  summarize(avg_bookings = mean(bookings),
            avg_booking_amount = mean(booking_amount),
            avg_booking_requests = mean(booking_requests),
            avg_property_page_views_per_visit = mean(property_page_views_visits),
            avg_displays_per_searchpage = mean(number_of_times_the_property_got_displayed_in_search_page)) %>% 
  ungroup() %>% 
  filter(post == 'Post')

# 690
control <- df_for_test %>% 
  filter(treatment == 0)

# 1294
treatment <- df_for_test %>% 
  filter(treatment == 1) %>% 
  sample_n(nrow(control))

df_for_test_resample <- control %>% 
  bind_rows(treatment)
```

Results:
* `avg_bookings`: not stat sig
* `avg_booking_amount`: not stat sig
* `avg_booking_requests`: stat sig (-0.00500467)
* `avg_property_page_views_per_visit`: stat sig (-1.85892)
* `avg_displays_per_searchpage`: not stat sig

```{r ttest}
# avg_bookings
# avg_booking_amount
# avg_booking_requests
# avg_property_page_views_per_visit
# avg_displays_per_searchpage

t.test(avg_displays_per_searchpage ~ treatment, 
       data = df_for_test_resample,
       var.equal = FALSE, 
       alternative = 'greater')
```

## 3. T-test (by location)

### 3.1. Texas

```{r resample_TX}
df_for_test <- metrics %>% 
  left_join(dplyr::select(property, property_id, location)) %>% 
  mutate(treatment = if_else(property_id %in% control_ids, 0, 1)) %>% 
  mutate(post = if_else(date < as.Date('2019-01-01'), 'Pre', 'Post')) %>% 
  group_by(property_id, location, post, treatment) %>% 
  summarize(avg_bookings = mean(bookings),
            avg_booking_amount = mean(booking_amount),
            avg_booking_requests = mean(booking_requests),
            avg_property_page_views_per_visit = mean(property_page_views_visits),
            avg_displays_per_searchpage = mean(number_of_times_the_property_got_displayed_in_search_page)) %>% 
  ungroup() %>% 
  filter(post == 'Post') %>% 
  filter(location == 'Austin, Texas')

control <- df_for_test %>% 
  filter(treatment == 0)

treatment <- df_for_test %>% 
  filter(treatment == 1) %>% 
  sample_n(nrow(control))

df_for_test_resample <- control %>% 
  bind_rows(treatment)
```

Results for Texas:
* `avg_bookings`: stat sig (-0.00898518)
* `avg_booking_amount`: not stat sig
* `avg_booking_requests`: stat sig (-0.01073499)
* `avg_property_page_views_per_visit`: not stat sig
* `avg_displays_per_searchpage`: not stat sig

```{r ttest_TX}
# avg_bookings
# avg_booking_amount
# avg_booking_requests
# avg_property_page_views_per_visit
# avg_displays_per_searchpage

t.test(avg_displays_per_searchpage ~ treatment, 
       data = df_for_test_resample,
       var.equal = FALSE, 
       alternative = 'greater')
```

### 3.2. Nevada

```{r resample_NV}
df_for_test <- metrics %>% 
  left_join(dplyr::select(property, property_id, location)) %>% 
  mutate(treatment = if_else(property_id %in% control_ids, 0, 1)) %>% 
  mutate(post = if_else(date < as.Date('2019-01-01'), 'Pre', 'Post')) %>% 
  group_by(property_id, location, post, treatment) %>% 
  summarize(avg_bookings = mean(bookings),
            avg_booking_amount = mean(booking_amount),
            avg_booking_requests = mean(booking_requests),
            avg_property_page_views_per_visit = mean(property_page_views_visits),
            avg_displays_per_searchpage = mean(number_of_times_the_property_got_displayed_in_search_page)) %>% 
  ungroup() %>% 
  filter(post == 'Post') %>% 
  filter(location == 'Vegas, Nevada')

control <- df_for_test %>% 
  filter(treatment == 0)

treatment <- df_for_test %>% 
  filter(treatment == 1) %>% 
  sample_n(nrow(control))

df_for_test_resample <- control %>% 
  bind_rows(treatment)
```

Results for Vegas:
* `avg_bookings`: not stat sig
* `avg_booking_amount`: weak stat sig (-25.36331)
* `avg_booking_requests`: weak stat sig (-0.00977751)
* `avg_property_page_views_per_visit`: not stat sig
* `avg_displays_per_searchpage`: not stat sig

```{r ttest_NV}
# avg_bookings
# avg_booking_amount
# avg_booking_requests
# avg_property_page_views_per_visit
# avg_displays_per_searchpage

t.test(avg_displays_per_searchpage ~ treatment, 
       data = df_for_test_resample,
       var.equal = FALSE, 
       alternative = 'greater')
```

### 3.3. Florida

```{r resample_FL}
df_for_test <- metrics %>% 
  left_join(dplyr::select(property, property_id, location)) %>% 
  mutate(treatment = if_else(property_id %in% control_ids, 0, 1)) %>% 
  mutate(post = if_else(date < as.Date('2019-01-01'), 'Pre', 'Post')) %>% 
  group_by(property_id, location, post, treatment) %>% 
  summarize(avg_bookings = mean(bookings),
            avg_booking_amount = mean(booking_amount),
            avg_booking_requests = mean(booking_requests),
            avg_property_page_views_per_visit = mean(property_page_views_visits),
            avg_displays_per_searchpage = mean(number_of_times_the_property_got_displayed_in_search_page)) %>% 
  ungroup() %>% 
  filter(post == 'Post') %>% 
  filter(location == 'Destin, Florida')

control <- df_for_test %>% 
  filter(treatment == 0)

treatment <- df_for_test %>% 
  filter(treatment == 1) %>% 
  sample_n(nrow(control))

df_for_test_resample <- control %>% 
  bind_rows(treatment)
```

Results for Florida:
* `avg_bookings`: not stat sig
* `avg_booking_amount`: not stat sig
* `avg_booking_requests`: not stat sig
* `avg_property_page_views_per_visit`: not stat sig
* `avg_displays_per_searchpage`: not stat sig

```{r ttest_NV}
# avg_bookings
# avg_booking_amount
# avg_booking_requests
# avg_property_page_views_per_visit
# avg_displays_per_searchpage

t.test(avg_displays_per_searchpage ~ treatment, 
       data = df_for_test_resample,
       var.equal = FALSE, 
       alternative = 'greater')
```


